---
output: html_fragment
---

## Cars observed during daily travel

This dynamic report shows observational logging data about cars that I observed during daily travel over multiple days. Each response represents one car that I noticed in a public place such as a road, car park, or traffic light area.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTokUGLCkRrq1n9V-vY5CtuG-FWeM93cjQdZ5LYBwczyB2ubH74aHCpPEh8mXwGiTNcRVFPSDk62bd2/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    date = time,
    car_type = `What type of car is it?`,
    colour = `What is the main colour of the car?`,
    occupants = `How many visible occupants are in the car?`,
    location = `Where did you observe the car?`
  )
```

### Summary of observations

The average number of visible occupants per car was `r round(mean(latest_data$occupants), 2)`.

The maximum number of visible occupants observed in one car was `r max(latest_data$occupants)`.

### Car types observed

```{r}
latest_data %>%
  ggplot(aes(x = car_type)) +
  geom_bar() +
  labs(
    title = "Number of cars observed by type",
    x = "Car type",
    y = "Count"
  )
```

### Car colours observed

```{r}
latest_data %>%
  ggplot(aes(x = colour)) +
  geom_bar() +
  labs(
    title = "Number of cars observed by colour",
    x = "Colour",
    y = "Count"
  )
```